---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zip

> Cross-Platform 'zip' Compression

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-lib/zip/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/zip/actions/workflows/R-CMD-check.yaml)
[![](https://www.r-pkg.org/badges/version/zip)](https://www.r-pkg.org/pkg/zip)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/zip)](https://www.r-pkg.org/pkg/zip)
[![Codecov test coverage](https://codecov.io/gh/r-lib/zip/graph/badge.svg)](https://app.codecov.io/gh/r-lib/zip)
<!-- badges: end -->

## Installation

Stable version:

```{r}
#| eval: false
install.packages("zip")
```

Development version:

```{r}
#| eval: false
pak::pak("r-lib/zip")
```

## Optional dependencies

* For progress bars (see below), the [cli](https://cli.r-lib.org) package
  is needed.
* Background processes, i.e. `zip_process()` and `unzip_process()`, need
  the [processx](https://processx.r-lib.org) package.

## Usage

```{r}
#| include: false
#| echo: false
#| results: hide
library(zip)
```

```{r}
library(zip)
```

### Creating ZIP files

`zip()` creates a new ZIP archive. (It overwrites the output file if it
exists.) Simply supply all directories and files that you want to include
in the archive.

It makes sense to change to the top-level directory of the files before
archiving them, so that the files are stored using a relative path name.

```{r}
zip("sources.zip", c("R", "src"))
file.info("sources.zip")
```

Directories are added recursively by default.

`zip_append()` is similar to `zip()`, but it appends files to an existing
ZIP archive.

### Listing ZIP files

`zip_list()` lists files in a ZIP archive. It returns a data frame:

```{r}
zip_list("sources.zip")
```

### Uncompressing ZIP files

`unzip()` uncompresses a ZIP archive:

```{r}
exdir <- tempfile()
unzip("sources.zip", exdir = exdir)
dir(exdir)
```

### Password-protected archives

Pass a `password` argument to encrypt entries with WinZip AES-256 (the
default), which is supported by 7-Zip, WinZip, and macOS Archive Utility:

```{r}
zip("secret.zip", "R", password = "hunter2")
zip_list("secret.zip")
unzip("secret.zip", exdir = tempfile(), password = "hunter2")
```

### Compressing and uncompressing in background processes

You can use the `zip_process()` and  `unzip_process()` functions to
create background zip / unzip processes. These processes were implemented
on top of the `processx::process` class, so they are pollable.

### Progress bars

`zip()` and `unzip()` (and co.) support progress bars if the `cli` package
is installed. This is disabled by default (for now), but can be enabled
by setting the `zip_progress` option or the `ZIP_PROGRESS` environment
variable to `TRUE`.

### Configuration

#### Options

* `zip_password`: The default password for ZIP encryption and decryption.
  Can be set to a string, a raw vector, or a function returning one.
* `zip_progress`: If set to `TRUE`, progress bars are enabled. Takes
  precedence over the `ZIP_PROGRESS` environment variable.

#### Environment variables

* `ZIP_PROGRESS`: If set to `TRUE`, progress bars are enabled. The
  `zip_progress` option takes precedence over this environment variable.

## License

MIT
